Measuring E-Mail Header Injections on the World Wide Web

### 2016-10-24 System/components.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

\subsubsection{Form Parser}
\label{Comp:FP}
The actual analysis pipeline begins at the Form Parser. This module is responsible for parsing the HTML and retrieving data about the HTML forms on the page, including the following:
\begin{itemize}
	\item Form attributes, such as \texttt{method} and \texttt{action} (URL) for the HTTP request.
	\item Data about the form input fields, such as their attributes, names, and default values. The default values are essential for fields like {\lstinline{<input type="hidden">}} as these fields are usually used to check for the submission of forms by bots.
	\item Presence of the {\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted (if the \texttt{action} attribute is a relative URL).
      % Adam: this is not correct, the referrer header won't be used when we make the request. We will set the referrer header when we make the request to URL that the form is on
	%% \item Headers associated with the page, such as \texttt{referrer}. Once again, these were required to avoid the website from ignoring our system as a bot.
\end{itemize} 
The Form Parser stores all this data in our database, so as to allow the system to reconstruct all data necessary for fuzzing the web application.

@@

\subsubsection{\Email Form Retriever}
\label{Comp:EMFR}
The \Email Form Retriever is the first stage in the Payload Injection module. It has the following functions:
\begin{itemize}
	\item Retrieve new forms and ensure no duplication occurs before the fuzzing stage.
	\item Reconstruct each form, using the stored form data, specifically the input fields and their values.
	\item Construct the target URL for the \texttt{action} attribute of the form to create an HTTP request to the correct URL for fuzzing. 
\end{itemize}

\subsubsection{Fuzzer}
\label{Comp:Fuzzer}
% Adam: we should call these something else but modules. We already have the top two modules, which are composed of components, now we need to split these into something (not components again). - DONE
The Fuzzer is the only component that interacts directly with the external web applications. The Fuzzer is split into smaller parts, each of which is responsible for a particular type of fuzzing.  The system injects payloads in two stages: the goal is to reduce the total number of HTTP requests the system generates to detect an \ehi vulnerability. Making HTTP requests is an expensive process~\cite{httpperf}, and can cause bottlenecks in a Crawler-Fuzzer system~\cite{ShkapenyukTorstenSuel2001}.
The two different types of payloads used for fuzzing are:
\paragraph{Non-Malicious Payload}
\label{Comp:Fuzzer:nmp}
The regular or non-malicious payload is simply an \email address. The goal is to see if the web application will send an \email message based on our input. The specific format of the \email is \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by an internal id that uniquely maps the payload to the form, and \texttt{example.com} is replaced by our domain.

\paragraph{Malicious Payload}
\label{Comp:Fuzzer:mp}
After receiving an \email from a specific form, we then use the malicious payload to try to exploit an \ehi vulnerability. We inject the form parameters with the \texttt{bcc} (blind carbon copy) header. If the vulnerability is present, this will cause the server to send a copy of the \email to the \email address we added as the \texttt{bcc} field.

@@

\end{enumerate}
The \texttt{(xxxx)} in each payload is replaced by an internal unique id to create a one-to-one mapping of the payloads to the forms.
% Adam: If we need to cut things for space, we can cut this next line and the payload coverage table.
The coverage provided by each payload is shown in Table~\ref{tab:payloadcov}.\\

@@

\begin{table}[tbp]
	\centering
	\normalsize
	\begin{tabular}{|c|c|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{Language/Platform}} & \multicolumn{1}{c}{\textbf{Unix}} & \multicolumn{1}{|c|}{\textbf{Windows}}\\
		\hline
		\textbf{PHP, Java, Ruby} & 1 & 3\\
		\hline
		\textbf{Python} & 2 & 4\\
		\hline
	\end{tabular}
	\caption[\titlecap{Payload coverage}]{Payload coverage, each payload covers a different platform/language.}
	\label{tab:payloadcov}
\end{table}

@@

\subsubsection{Injection Verification}
\label{Comp:EMA}
The Injection Verification module checks for the presence of injected data in the received \emails. This module works on the \emails received and stored by our Postfix server, and, depending on the user account that received the \email, it performs different functions.
\paragraph{Analyzing regular e-mail}
\sloppy
`Regular \email' refers to the \emails received by account {\lstinline{reguser(xxxx)@example.com}} that were sent due to injecting the regular, non-malicious, payload (discussed in Section~\ref{Comp:Fuzzer:nmp}). The objective of the analysis on this \email is identify if the input fields that we injected with data appear on the resulting \email, and if so, which fields appear where.

@@

\paragraph{Analyzing \email with payloads}
The ``\emails with payloads'' refers to \emails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@example.com}} accounts. These \emails could only be received as a result of injecting the malicious payloads that were discussed in Section~\ref{Comp:Fuzzer:mp}.

\paragraph{Detecting injected \texttt{bcc} headers}
As discussed in the payloads section~(\ref{Comp:Fuzzer:mp}), the payloads were crafted such that the \emails received by the \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field.

\label{analyze:detect_x_check}
\paragraph{Detecting injected \texttt{x-check} headers}
\Emails not received by the \texttt{maluser} account but by the \texttt{nuser} account constitute a special category of \emails.
These \emails could have been generated due to two reasons:
\begin{enumerate}
	\item The web application performed some sanitization routines and stripped out the \texttt{bcc} part of the payload, thereby sending \emails only to the \texttt{nuser} account. These \emails then act as proof that the vulnerability was not found on the given URL.
	\item The \texttt{bcc} header can be ignored for other reasons (e.g.,\ Python's default behavior when it encounters duplicate headers). In this case, we check if the \email contains the custom header \texttt{x-check}. If it does, then this is a successful exploit of the vulnerability.
\end{enumerate}

>>>>

\subsubsection{Form Parser}
\label{Comp:FP}
The actual analysis pipeline begins at the Form Parser. This module is
responsible for parsing the HTML and retrieving data about the HTML
forms on the page, including the following: (1) Form attributes, such
as \texttt{method} and \texttt{action} (URL) for the HTTP request, (2)
Data about the form input fields, such as their attributes, names, and
default values. The default values are essential for fields like
{\lstinline{<input type="hidden">}} as these fields are usually used
to check for the submission of forms by bots, and (3) Presence of the {\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted (if the \texttt{action} attribute is a relative URL).
      % Adam: this is not correct, the referrer header won't be used when we make the request. We will set the referrer header when we make the request to URL that the form is on
	%% \item Headers associated with the page, such as \texttt{referrer}. Once again, these were required to avoid the website from ignoring our system as a bot.

@@

\subsubsection{\Email Form Retriever}
\label{Comp:EMFR}
The \Email Form Retriever is the first stage in the Payload Injection
module. It has the following functions: (1) Retrieve new forms and
ensure no duplication occurs before the fuzzing stage, (2) reconstruct
each form, using the stored form data, specifically the input fields
and their values, and (3) construct the target URL for the
\texttt{action} attribute of the form to create an HTTP request to the
correct URL for fuzzing.

\subsubsection{Fuzzer}
\label{Comp:Fuzzer}
% Adam: we should call these something else but modules. We already have the top two modules, which are composed of components, now we need to split these into something (not components again). - DONE
The Fuzzer is the only component that interacts directly with the external web applications. The Fuzzer is split into smaller parts, each of which is responsible for a particular type of fuzzing.  The system injects payloads in two stages: the goal is to reduce the total number of HTTP requests the system generates to detect an \ehi vulnerability. Making HTTP requests is an expensive process~\cite{httpperf}, and can cause bottlenecks in a Crawler-Fuzzer system~\cite{ShkapenyukTorstenSuel2001}.
The two different types of payloads used for fuzzing are:

\noindent\textbf{Non-Malicious Payload.}
The regular or non-malicious payload is simply an \email address. The goal is to see if the web application will send an \email message based on our input. The specific format of the \email is \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by an internal id that uniquely maps the payload to the form, and \texttt{example.com} is replaced by our domain.

\noindent\textbf{Malicious Payload.}
After receiving an \email from a specific form, we then use the malicious payload to try to exploit an \ehi vulnerability. We inject the form parameters with the \texttt{bcc} (blind carbon copy) header. If the vulnerability is present, this will cause the server to send a copy of the \email to the \email address we added as the \texttt{bcc} field.

@@

\end{enumerate}
The \texttt{(xxxx)} in each payload is replaced by an internal unique id to create a one-to-one mapping of the payloads to the forms.
% Adam: If we need to cut things for space, we can cut this next line and the payload coverage table.

@@

%% \begin{table}[tbp]
%% 	\centering
%% 	\scriptsize
%% 	\begin{tabular}{|c|c|c|}
%% 		\hline
%% 		\multicolumn{1}{|c|}{\textbf{Language/Platform}} & \multicolumn{1}{c}{\textbf{Unix}} & \multicolumn{1}{|c|}{\textbf{Windows}}\\
%% 		\hline
%% 		\textbf{PHP, Java, Ruby} & 1 & 3\\
%% 		\hline
%% 		\textbf{Python} & 2 & 4\\
%% 		\hline
%% 	\end{tabular}
%% 	\caption[\titlecap{Payload coverage}]{Payload coverage, each payload covers a different platform/language.}
%% 	\label{tab:payloadcov}
%% \end{table}

@@

\subsubsection{Injection Verification}
\label{Comp:EMA}
The Injection Verification module checks for the presence of injected data in the received \emails. This module works on the \emails received and stored by our Postfix server, and, depending on the user account that received the \email, it performs different functions.

\noindent\textbf{Analyzing regular e-mail.}
\sloppy
`Regular \email' refers to the \emails received by account {\lstinline{reguser(xxxx)@example.com}} that were sent due to injecting the regular, non-malicious, payload (discussed in Section~\ref{Comp:Fuzzer}). The objective of the analysis on this \email is identify if the input fields that we injected with data appear on the resulting \email, and if so, which fields appear where.

@@

\noindent\textbf{Analyzing \email with payloads}
The ``\emails with payloads'' refers to \emails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@example.com}} accounts. These \emails could only be received as a result of injecting the malicious payloads that were discussed in Section~\ref{Comp:Fuzzer}.

\noindent\textbf{Detecting injected \texttt{bcc} headers}
As discussed in the payloads Section~(\ref{Comp:Fuzzer}), the payloads were crafted such that the \emails received by the \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field.

\label{analyze:detect_x_check}
\noindent\textbf{Detecting injected \texttt{x-check} headers}
\Emails not received by the \texttt{maluser} account but by the \texttt{nuser} account constitute a special category of \emails.
These \emails could have been generated due to two reasons:
\begin{enumerate}
	\item The web application performed some sanitization routines and stripped out the \texttt{bcc} part of the payload, thereby sending \emails only to the \texttt{nuser} account. These \emails then act as proof that the vulnerability was not found on the given URL.
	\item The \texttt{bcc} header can be ignored for other reasons (e.g.,\ Python's default behavior when it encounters duplicate headers). In this case, we check if the \email contains the custom header \texttt{x-check}. If it does, then this is a successful exploit of the vulnerability.
\end{enumerate}

### 2016-10-24 System/proof_of_concept.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

The front-end for each of the three applications is shown in Listing~\ref{code:html}. The server-side code for PHP, Python, and Ruby is shown in Listings~\ref{code:phpemi}, \ref{code:pyemi}, and \ref{code:rubyemi} respectively.

@@

%% The astute reader might have noticed that in the given example we have used \texttt{\%0a} to separate the headers, while in Section~\ref{Comp:Fuzzer:mp}, we had used \texttt{\textbackslash{}n}. This is due to URL encoding~\cite{rfc1738}, wherein special characters in th URL are `encoded' or `escaped' with their ASCII equivalent.
%% The reason why we do not have to do this with the payloads our system injects is due to the fact that the Python Requests library that we use to generate the HTTP requests automatically does this encoding for us.

\begin{lstlisting}[language=HTML,caption={HTML page for showcasing
      \ehi, a simple front-end for our
      examples.},label={code:html}, float]
<!doctype html>
<html lang="en">
<head>
<meta charset="utf-8">
<meta name="author" content="XYZ">
<title>Mock Email</title>
</head>
<body>
<form action="script-path" method="post">
<input type="text" name="email">
<textarea name="msg"></textarea>
<input type="submit" value="Email Me!">
</form></body></html>
\end{lstlisting}
\input{Background/ruby}

>>>>

The server-side code for PHP is shown in Listings~\ref{code:phpemi},
while the Python and Ruby code is not shown for space limitations.

@@

%% The astute reader might have noticed that in the given example we have used \texttt{\%0a} to separate the headers, while in Section~\ref{Comp:Fuzzer}, we had used \texttt{\textbackslash{}n}. This is due to URL encoding~\cite{rfc1738}, wherein special characters in th URL are `encoded' or `escaped' with their ASCII equivalent.
%% The reason why we do not have to do this with the payloads our system injects is due to the fact that the Python Requests library that we use to generate the HTTP requests automatically does this encoding for us.

%% \begin{lstlisting}[language=HTML,caption={HTML page for showcasing
%%       \ehi, a simple front-end for our
%%       examples.},label={code:html}, float]
%% <!doctype html>
%% <html lang="en">
%% <head>
%% <meta charset="utf-8">
%% <meta name="author" content="XYZ">
%% <title>Mock Email</title>
%% </head>
%% <body>
%% <form action="script-path" method="post">
%% <input type="text" name="email">
%% <textarea name="msg"></textarea>
%% <input type="submit" value="Email Me!">
%% </form></body></html>
%% \end{lstlisting}
%\input{Background/ruby}

### 2016-10-24 System/sys_arch.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

The Data Gathering module is responsible for the following activities:
	\begin{itemize}
		\item Interface with the Crawler (Section~\ref{Comp:Crawler}) and receive the URLs.
		\item Parse the HTML for the corresponding URL and store the relevant form data (Section~\ref{Comp:FP}).
		\item Check for the presence of HTML forms that could allow a user to send/receive \email and store references to these forms (Section~\ref{Comp:EMFC}).
	\end{itemize}

	The Payload Injection module is responsible for the following activities:
	\begin{itemize}
		\item Retrieve the HTML forms that could allow a user to send/receive \email and reconstruct these forms (Section~\ref{Comp:EMFR}).
		\item Inject these forms with benign data (non-malicious payloads) and generate an HTTP request to the corresponding URL (Section~\ref{Comp:Fuzzer:nmp}).
		\item Analyze the received \emails, extracting the \email header fields and checking for the presence of the injected payloads (Section~\ref{Comp:EMA}).
		\item Inject the HTTP requests that sent us \emails with malicious payloads, and generate an HTTP request to the corresponding URL to check if an \ehi vulnerability exists in that web application (Section~\ref{Comp:Fuzzer:mp}).
	\end{itemize} 
	%% The functionality of each component is discussed further in the `Components' section (Section~\ref{Comp}). The Payload Injection pipeline is not a linear, but cyclic process, as we inject different payloads and analyze the received \emails.

>>>>

The Data Gathering module is responsible for the following activities:
(1) Interface with the Crawler (Section~\ref{Comp:Crawler}) and
receive the URLs, (2) Parse the HTML for the corresponding URL and
store the relevant form data (Section~\ref{Comp:FP}), and (3) Check
for the presence of HTML forms that could allow a user to send/receive
\email and store references to these forms (Section~\ref{Comp:EMFC}).

The Payload Injection module is responsible for the following
activities: (1) Retrieve the HTML forms that could allow a user to
send/receive \email and reconstruct these forms
(Section~\ref{Comp:EMFR}), (2) Inject these forms with benign data
(non-malicious payloads) and generate an HTTP request to the
corresponding URL (Section~\ref{Comp:Fuzzer}), (3) Analyze the
received \emails, extracting the \email header fields and checking for
the presence of the injected payloads (Section~\ref{Comp:EMA}), and
(4) Inject the HTTP requests that sent us \emails with malicious
payloads, and generate an HTTP request to the corresponding URL to
check if an \ehi vulnerability exists in that web application
(Section~\ref{Comp:Fuzzer}).

	%% The functionality of each component is discussed further in the `Components' section (Section~\ref{Comp}). The Payload Injection pipeline is not a linear, but cyclic process, as we inject different payloads and analyze the received \emails.

### 2016-10-24 paper.tex
final data update
Edits to abstract
Edits to the introduction
fixed the todos in intro, abstract and background added paragraph and ref to smtp, added ref to command injection changed domains to example.com
Halfway through System Section
Edited through the results section
fixed todos in evaluation
fixed todos in discussion
added the exploitation evidence section
updated with new email
updated for WWW paper
added virus email attachments section
almost at 13 pages, need to bering it to 9
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of

@@

% default options for listings
\usepackage{listings}
\usepackage{listingsutf8}
\usepackage{textcomp}     % access \textquotesingle
\lstset{
	backgroundcolor=\color{lightgray},
	basicstyle=\ttfamily,
	breaklines=true, 
	captionpos=b,
	commentstyle=\color{darkgreen}, 
	frame=single,
	keywordstyle=\color{blue}, 
	numbers=left,
	numbersep=5pt,
	numberstyle=\tiny\color{mygray},
	rulecolor=\color{black},
	showstringspaces=false,
	upquote=true
}

\newcommand{\dq}[1]{``{#1}''}
%% THIS IS THE DATA FOR OUR THESIS, UPDATING HERE WILL UPDATE EVERYWHERE %%
\newcommand{\urls}{21,675,680}

\newcommand{\forms}{6,794,917}
\newcommand{\formsDelta}{31.35\%}

\newcommand{\emailforms}{1,132,157}
\newcommand{\emailformsDelta}{16.66\%}

\newcommand{\fuzzed}{934,016}
\newcommand{\fuzzedDelta}{82.50\%}

\newcommand{\recd}{52,724}
\newcommand{\recdDelta}{5.64\%}

\newcommand{\malfuzzed}{46,156}
\newcommand{\malfuzzedDelta}{87.54\%}

\newcommand{\success}{496}
\newcommand{\successDelta}{1.07\%}

\newcommand{\domains}{222}
\newcommand{\ips}{292}
% these refer to unique domains, not unique forms
\newcommand{\uniqueforms}{1,019,921}
\newcommand{\uniqueemailforms}{197,570}

@@

	%\title{E-jection fraction - Tracking how your website pumps out
	%E-Mails}
    \title{The Prevalence of E-Mail Header Injections on the World
      Wide Web}
	%
	% You need the command \numberofauthors to handle the 'placement
	% and alignment' of the authors beneath the title.
	%
	% For aesthetic reasons, we recommend 'three authors at a time'
	% i.e. three 'name/affiliation blocks' be placed beneath the title.
	%
	% NOTE: You are NOT restricted in how many 'rows' of
	% "name/affiliations" may appear. We just ask that you restrict
	% the number of 'columns' to three.
	%
	% Because of the available 'opening page real-estate'
	% we ask you to refrain from putting more than six authors
	% (two rows with three columns) beneath the article title.
	% More than six makes the first-page appear very cluttered indeed.
	%
	% Use the \alignauthor commands to handle the names
	% and affiliations for an 'aesthetic maximum' of six authors.
	% Add names, affiliations, addresses for
	% the seventh etc. author(s) as the argument for the
	% \additionalauthors command.
	% These 'additional authors' will be output/set for you
	% without further effort on your part as the last section in
	% the body of your article BEFORE References or any Appendices.

@@

    % Note: For CCS submission we need to have it anonymous

@@

	\input{exp_setup}

@@

	%
	% The following two commands are all you need in the
	% initial runs of your .tex file to
	% produce the bibliography for the citations in your paper.
	\bibliographystyle{abbrv}
	\bibliography{biblio}  
	% You must have a proper ".bib" file
	%  and remember to run:
	% latex bibtex latex latex
	% to resolve all references
	%
	%\balancecolumns
\end{document}

>>>>

% Great package for spaces in commands
\usepackage{xspace}

@@

% default options for listings
\usepackage{listings}
\usepackage{listingsutf8}
\usepackage{textcomp}     % access \textquotesingle
\lstset{
	backgroundcolor=\color{lightgray},
	basicstyle=\scriptsize{}\ttfamily,
	breaklines=true, 
	captionpos=b,
	commentstyle=\color{darkgreen}, 
	frame=single,
	keywordstyle=\color{blue}, 
	numbers=left,
	numbersep=5pt,
	numberstyle=\tiny\color{mygray},
	rulecolor=\color{black},
	showstringspaces=false,
	upquote=true
}

% Important for the layout
\clubpenalty=10000
\widowpenalty=10000

\newcommand{\dq}[1]{``{#1}''}
%% THIS IS THE DATA FOR OUR THESIS, UPDATING HERE WILL UPDATE EVERYWHERE %%
\newcommand{\urls}{23,553,796\xspace}

\newcommand{\forms}{7,354,425\xspace}
\newcommand{\formsDelta}{31.22\%\xspace}

\newcommand{\emailforms}{1,228,774\xspace}
\newcommand{\emailformsDelta}{16.71\%\xspace}

\newcommand{\fuzzed}{1,012,530\xspace}
\newcommand{\fuzzedDelta}{82.40\%\xspace}

\newcommand{\recd}{74,192\xspace}
\newcommand{\recdDelta}{7.33\%\xspace}

\newcommand{\diffFoundFuzz}{9,682\xspace}
\newcommand{\malfuzzed}{64,510\xspace}
\newcommand{\malfuzzedDelta}{86.95\%\xspace}

\newcommand{\success}{994\xspace}
\newcommand{\successDelta}{1.54\%\xspace}
\newcommand{\successWebsitesDelta}{0.038\%\xspace} % calc domains/total_domains 414/1,085,365

\newcommand{\slowSelenium}{31.58\%\xspace}
\newcommand{\slowParse}{11.05\%\xspace}

\newcommand{\domains}{414\xspace}
\newcommand{\ips}{604\xspace}

\newcommand{\emailedDefaultmailbox}{113\xspace}
\newcommand{\responses}{21\xspace}
\newcommand{\confirmed}{15\xspace}

\newcommand{\ipsblacklist}{157\xspace}
\newcommand{\ipsblacklistmulti}{46\xspace}

\newcommand{\ehibcc}{583\xspace}
\newcommand{\ehixcheck}{493\xspace}
\newcommand{\ehito}{229\xspace}
\newcommand{\ehibccxcheck}{310\xspace}
\newcommand{\ehitoxcheck}{15\xspace}
\newcommand{\ehinuserxcheck}{239\xspace}
\newcommand{\ehiuniquenuserxcheck}{182\xspace}

% these refer to unique domains, not unique forms
\newcommand{\uniqueforms}{1,085,365\xspace}
\newcommand{\uniqueemailforms}{198,306\xspace}

\newcommand{\totalattachmentcount}{2,950\xspace}
\newcommand{\totalvirusattachmentcount}{265\xspace}
\newcommand{\totalvirusemails}{443\xspace}

\newcommand{\ehi}{E-\nobreak{}mail Header Injection\xspace}
\renewcommand{\email}{e-\nobreak{}mail\xspace}
\newcommand{\emails}{\email{}s\xspace}
\newcommand{\emailed}{\email{}ed\xspace}    
\newcommand{\Email}{E-\nobreak{}mail\xspace}        
\newcommand{\Emails}{\Email{}s\xspace}

@@

	%\title{E-jection fraction - Tracking how your website pumps out
	%E-Mails}
    \title{Measuring E-Mail Header Injections on the World
    	Wide Web}
	%
	% You need the command \numberofauthors to handle the 'placement
	% and alignment' of the authors beneath the title.
	%
	% For aesthetic reasons, we recommend 'three authors at a time'
	% i.e. three 'name/affiliation blocks' be placed beneath the title.
	%
	% NOTE: You are NOT restricted in how many 'rows' of
	% "name/affiliations" may appear. We just ask that you restrict
	% the number of 'columns' to three.
	%
	% Because of the available 'opening page real-estate'
	% we ask you to refrain from putting more than six authors
	% (two rows with three columns) beneath the article title.
	% More than six makes the first-page appear very cluttered indeed.
	%
	% Use the \alignauthor commands to handle the names
	% and affiliations for an 'aesthetic maximum' of six authors.
	% Add names, affiliations, addresses for
	% the seventh etc. author(s) as the argument for the
	% \additionalauthors command.
	% These 'additional authors' will be output/set for you
	% without further effort on your part as the last section in
	% the body of your article BEFORE References or any Appendices.

@@

    % Note: For CCS submission we need to have it anonymous
    % The author list will be:
    % Sai, Pierre-Marie, Giovanni, Ziming, Adam, Gail

@@

%	\input{exp_setup}

@@

	%
	% The following two commands are all you need in the
	% initial runs of your .tex file to
	% produce the bibliography for the citations in your paper.
	\bibliographystyle{abbrv}
	{\scriptsize\bibliography{biblio}}
%	\bibliography{biblio}  
	% You must have a proper ".bib" file
	%  and remember to run:
	% latex bibtex latex latex
	% to resolve all references
	%
	%\balancecolumns
\end{document}
